Religion and Its Influence on Social Issues^[Code and data are available at: https://github.com/dudqo/religion_survey]

### 2022-04-23 outputs/paper/paper.Rmd
ggplot

```{r fig3, echo = FALSE, fig.cap= "Distribution of survey respondents' gender"}
reduced_data %>%
  ggplot(aes(x = gender, fill = relig)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' Gender",
       ) +
  theme(legend.position = "none")
```

@@

```{r fig8, echo=FALSE, fig.cap = "Distribution of religion of survey respondents"}
reduced_data %>%
  drop_na(Assistance_to_the_poor) %>%
  ggplot(aes(x = relig, fill = Assistance_to_the_poor)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government spending enough on coditions of Black People?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

>>>>

```{r fig3, echo = FALSE, fig.cap= "Distribution of survey respondents' gender"}
reduced_data %>%
  ggplot(aes(x = gender, fill = relig)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' Gender",
       ) +
  theme(legend.title = element_blank()) +
  coord_flip() +
  facet_wrap(~opsex)
```

@@

```{r fig8, echo=FALSE, fig.cap = "Distribution of religion of survey respondents"}
reduced_data %>%
  drop_na(Assistance_to_the_poor) %>%
  ggplot(aes(x = relig, fill = Assistance_to_the_poor)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough to Asssist the Poor?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```
```{r fig9, echo=FALSE, fig.cap = "Distribution of religion of survey respondents"}
reduced_data %>%
  drop_na(social_security) %>%
  ggplot(aes(x = relig, fill = social_security)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough to Asssist the Poor?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```
```{r fig10, echo=FALSE, fig.cap = "Distribution of religion of survey respondents"}
reduced_data %>%
  drop_na(natcrime) %>%
  ggplot(aes(x = relig, fill = natcrime)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough to Asssist the Poor?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```
```{r fig11, echo=FALSE, fig.cap = "Distribution of religion of survey respondents"}
reduced_data %>%
  drop_na(Immigration) %>%
  ggplot(aes(x = relig, fill = Immigration)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough to Asssist the Poor?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```

```{r fig12, echo=FALSE, fig.cap = "Distribution of religion of survey respondents"}
reduced_data %>%
  drop_na(religinf) %>%
  ggplot(aes(x = relig, fill = religinf)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough to Asssist the Poor?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```
```{r fig13, echo=FALSE, fig.cap = "Distribution of religion of survey respondents"}
reduced_data %>%
  drop_na(opsex) %>%
  ggplot(aes(x = relig, fill = opsex)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the Government Spending Enough to Asssist the Poor?",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```
